%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Analytics Advisor, Data Science} % Job title
    {Direct Supply, Inc.} % Organization
    {Milwaukee, Wis.} % Location
    {March 2017 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Within first 30 days of joining team, built an LDA Topic Model that predicted what free-form text-based work orders were "about", allowing engineering to trigger real time advertising on topical key words entered by mobile app users (R::topicmodels).}
        \item {Designed, built, and evaluated a system that generates recurring monthly call and email campaigns by targeting customers most likely to buy in timeframe using logistic regression. Achieved 13 percentage "point" boost in clicks and 5 percentage "point" increase in purchase rate over a 20\% holdout group in first 12 months in production (R::stats::glm).}
        \item {Estimated causal effect of a new product line on existing margin using bayesian structural timeseries models (in absence of randomized experiment), enabling product managers to proceed to rollout more product (R::CausalImpact).}
        \item {Predicted date range a skilled nursing facility was to be inspected with 85\% accuracy using Stratified Cox survival model to monetize publically available data from the Centers for Medicare \& Medicaid Services (CMS) (R::survival).}
        \item {Automated the analysis of a biannual Net Promoter Score survey in R (was living in SPSS), reducing 280 hours of work from 1.5 FTE’s to 14 hours of work by 1 FTE using custom-developed library of R functions.}
        \item {Helped eCommerce executive leadership meet their KPI of retaining, growing, and finding customers by visualizing a time series of customer lifecycle (new, full, lapsed)(R::TraMineR).}
        \item {Estimated opportunity cost of discontinuing support of Internet Explorer 8 to help IT assess impact.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Business Intelligence Analyst, Data Science} % Job title
    {Direct Supply, Inc.} % Organization
    {Milwaukee, Wis.} % Location
    {Dec. 2015 - March 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Authored an Abandonded Shopping Cart Report that informed sellers when customers in territory placed product in shopping cart but hadn't purchased yet, which led to a 4 percentage "point" lift in sales.}
        \item {Authored complex SQL queries/views/functions and reports to meet key KPIs, which varied across teams, departments, and business units.}
        \item {Acted as an advisor to stakeholders by having knowledge of data structures and system capabilities.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Reporting Analyst Intern, Data Science} % Job title
    {Direct Supply, Inc.} % Organization
    {Milwaukee, Wis.} % Location
    {Oct. 2014 - Dec. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Fulfilled reporting requests by building and updating reports and dashboards using T-SQL, SSRS, and Microsoft Visual Studio.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Economics Research Assistant, Undergraduate Research Fellowship} % Job title
    {University of Wisconsin - Milwaukee} % Organization
    {Milwaukee, Wis.} % Location
    {Sept. 2014 - Dec. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Performed tasks to advance the research project of addressing whether the 5 cent plastic bag tax in Washington D.C. led to a decrease in food consumption, under the guidance of Dr. Laura Grant.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Math Basics Coordinator, Intern} % Job title
    {Literacy Services of Wisconsin} % Organization
    {Milwaukee, Wis.} % Location
    {May 2014 - Aug. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a new curriculum of basic math courses for adult students and taught all math lessons 1:1.}
      \end{cvitems}
    }
%---------------------------------------------------------   
\end{cventries}